Approximation as Differentiation

### 2025-06-28 main/language.tex
Put inductive types experiment in a subfolder.
Rehashing without inductive types.

% \input{fig/mu-polynomial}
\input{fig/semantics-parameterised-types}
\input{fig/semantics}

@@

To give the semantics for the language defined in \figrefTwo{syntax}{typing}, we fix a bicartesian closed
category $\Sem$ with finite products $(\times, 1)$, finite coproducts $(\coprod, 0)$, exponentials
$\internalHom{X}{Y}$, evaluation morphisms $\eval_{X,Y}$ and currying isomorphisms $\lambda_{X,Y,Z}$, plus the
following additional structure:
\begin{enumerate}
\item a strong monad $\mathcal{L}$ (lifting) with unit $\eta_X: X \to \mathcal{L}(X)$, multiplication $\mu_X:
\mathcal{L}^2(X) \to \mathcal{L}(X)$ and strength $\mathsf{st}_{X,Y}: X \times \mathcal{L}(Y) \to
\mathcal{L}(X \times Y)$;
% \item $\mu$-polynomial endofunctors given by $\muPoly_{\Sem}$;
\item for each primitive type $\rho \in \PrimTy$, an object $\sem{\rho}$;
\item for each primitive operation $\phi \in \PrimOp^\rho_{\rho_1,\ldots,\rho_n}$, a morphism $\sem{\phi}:
\sem{\rho_1} \times \ldots \times \sem{\rho_n} \to \sem{\rho}$.
\end{enumerate}

\figref{semantics:types} gives the interpretation of types $\Delta \vdash \tau$ with $\length{\Delta}
= n$ as functors $\Sem^n \to \Sem$, or as objects of $\Sem$ in the case $n = 0$.
\figref{semantics:terms} gives the interpretation of terms $\Gamma \vdash t: \tau$ as morphisms
$\sem{\Gamma} \to \sem{\tau}$.

>>>>

% \input{fig/mu-polynomial}
% \input{fig/inductive-types/semantics}
\input{fig/semantics}

@@

To give the semantics for the language defined in \figrefTwo{syntax}{typing}, we fix a bicartesian closed
category $\Sem$ with finite products $(\times, 1)$, finite coproducts $(\coprod, 0)$ and exponentials
$\internalHom{X}{Y}$, with evaluation morphisms $\eval_{X,Y}$ and currying isomorphisms $\lambda_{X,Y,Z}$,
plus the following additional structure:
\begin{enumerate}
\item a strong monad $\mathcal{L}$ (lifting) with unit $\eta_X: X \to \mathcal{L}(X)$, multiplication $\mu_X:
\mathcal{L}^2(X) \to \mathcal{L}(X)$ and strength $\mathsf{st}_{X,Y}: X \times \mathcal{L}(Y) \to
\mathcal{L}(X \times Y)$;
% \item $\mu$-polynomial endofunctors given by $\muPoly_{\Sem}$;
\item for each primitive type $\rho \in \PrimTy$, an object $\sem{\rho}_{\PrimTy}$;
\item for each primitive operation $\phi \in \PrimOp^\rho_{\rho_1,\ldots,\rho_n}$, a morphism $\sem{\phi}:
\sem{\rho_1} \times \ldots \times \sem{\rho_n} \to \sem{\rho}$.
\end{enumerate}

% \figref{semantics:types} gives the interpretation of types $\Delta \vdash \tau$ with $\length{\Delta}
% = n$ as functors $\Sem^n \to \Sem$, or as objects of $\Sem$ in the case $n = 0$.
\figrefTwo{semantics:types}{semantics:contexts} give the interpretations of types $\tau$ and contexts $\Gamma$
as objects of $\Sem$. \figref{semantics:terms} gives the interpretation of terms $\Gamma \vdash t: \tau$ as
morphisms $\sem{\Gamma} \to \sem{\tau}$.
